---
title: "Assignment7"
author: "Parth Shah"
date: "21/10/2021"
output: html_document
---
## Importing Libraries
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(data.table)
library(haven)
library(tidyverse)
library(tidyquant)
library(tidyr)
library(lubridate)
library(naniar)
library(readxl)
library(plotly)
library(scales)
library(fredr)
library(openxlsx)
library(fredr)
library(zoo)
library(frenchdata)
library(NMOF)
library(datetimeutils)
library(lme4)
library(geckor)
library(tibbletime)
library(zeallot)
library(sandwich)
library(lmtest)
library(tidyquant)

```

## Fama French Data 
We extract fama french data.
It contains the risk free interest rate, High minus low premium, small minus big premium, and market risk premium.
```{r}
french_data <- French(getwd(),dataset = "F-F_Research_Data_Factors_CSV.zip")

french_data$DATE <- row.names(french_data)
rownames(french_data) <- NULL
french_data <- french_data %>% 
  mutate(DATE = as.Date(DATE)) %>%
  mutate(RF = as.numeric(RF),
        HML = as.numeric(HML),
        SMB = as.numeric(SMB),
        MKTRF = as.numeric(`Mkt-RF`),
        DATE = floor_date(DATE, unit = "month"))

```

## Defining functions
```{r}
getReturns <- function(yearly_portfolio_returns) {

  cum_returns <- yearly_portfolio_returns %>%
              group_by(quintiles) %>%
              mutate(Eq_cum_returns = Eq_yearly_returns,
                     Wtd_cum_return = Weighted_yearly_returns,
                     market_cum_return = mkt_excess_return) %>%
              select(c(year, quintiles,Eq_cum_returns, Wtd_cum_return, market_cum_return)) %>%
              ungroup()
}

getRankedStocks <- function(data, variable) {
    index_ranking <- data %>% drop_na(variable) %>%
              mutate(fyear = as.Date(paste(fyear, 1, 1, sep = "-"))) %>% 
              group_by(fyear) %>%  mutate(quintiles = ntile(!!sym(variable),5))
}

getRankedStocks_forcleandate <- function(data, variable) {
    index_ranking <- data %>% drop_na(variable) %>%
              group_by(fyear) %>%  mutate(quintiles = ntile(!!sym(variable),5))
}

calcCumRets <- function(index_ranking, yearly_returns,variable) {
  yearly_data_ranked <- yearly_returns %>%
                inner_join(index_ranking,  by = c("year" = "fyear", "CUSIP" = "cusip")) %>%
                drop_na(quintiles) 
  yearly_portfolio_returns <- yearly_data_ranked %>% 
              drop_na(quintiles) %>%
              select(c("year", "CUSIP", "cum_excess_return", "market_cum_return","cum_ln_ret" ,variable, "quintiles")) %>%
              group_by(year, quintiles) %>%
              summarise(Eq_yearly_returns = mean(cum_excess_return,na.rm=TRUE),
                        mkt_excess_return = mean(market_cum_return, na.rm=TRUE),
                        Weighted_yearly_returns = weighted.mean(cum_excess_return,!!sym(variable), na.rm = TRUE)) %>%
              ungroup()
  cum_returns <- yearly_portfolio_returns %>%
              group_by(quintiles) %>%
              mutate(Eq_cum_returns = cumprod(1+Eq_yearly_returns)-1,
                     Wtd_cum_return = cumprod(1+Weighted_yearly_returns)-1,
                     market_cum_return = cumprod(1+mkt_excess_return)-1) %>%
              select(c(year, quintiles,Eq_cum_returns, Wtd_cum_return, market_cum_return)) %>%
              ungroup()
}

data_plot = function(master_data_join, datatype) {
  len <- dim(master_data_join)
  plot <- master_data_join %>% plot_ly()
  
  for(i in seq_along(master_data_join)) {
    if (i<2) {next} else{  
      x <- plot %>% add_trace(x = ~year, y=master_data_join[[i]] ,mode = 'bar', name=colnames(master_data_join)[i])
    }
    plot <- x
  }
  
  plot %>% 
    layout(title     = datatype,
         barmode   = 'relative',
         xaxis     = list(title=''),
         margin    = list(l = 75, r = 75, b = 50, t = 50, pad = 4),
         xaxis     = list(title = ""),
         yaxis     = list(side = 'left', title = "Returns", showgrid = TRUE, zeroline = TRUE, color = 'steelblue'),
         legend = list(traceorder = 'reversed',orientation = "h"))
}

## to plot recession periods over a plot
## taken from john regenstiens session
recession_shade_fun <- function(color_chosen = "darkgray", start_date = "1970-01-01"){
  "USREC" %>%
  tq_get(get = "economic.data", from = start_date) %>%
  rename(year = date)%>%
  select(year, recession_flag = price) %>%
  mutate(recession_label = case_when(recession_flag == 1 & lag(recession_flag == 0) ~ str_glue("{year(year)} recession"),
         TRUE ~ NA_character_)) %>%
  filter(recession_flag == 1) %>%
  fill(recession_label, .direction = "down") %>%
  group_by(recession_label) %>%
  slice(1, n()) %>%
  select(-recession_flag) %>%
  mutate(start = case_when(year == min(year) ~ year,
                           TRUE ~ NA_Date_),
         end = case_when(year == max(year) ~ year,
                         TRUE ~ NA_Date_),
         end = lead(end)
         ) %>%
  filter(!is.na(start)) %>%
  select(-year) %>%
    geom_rect(data = .,
            inherit.aes = F,
            aes(xmin = start,
                xmax = end,
                ymin = -Inf,
                ymax = +Inf),
            fill = color_chosen,
            alpha = 0.4)
}

plot_with_recession <- function(data, datatype) {
  df <- melt(data ,  id.vars = 'year', variable.name = 'Portfolio')
  df = df%>%
    rename(Returns = value)%>%
    drop_na(Returns)
ggplot(df, aes(x = year, y = Returns, colour = Portfolio)) +
  geom_line()+ recession_shade_fun() +theme_minimal()+
  ggtitle(datatype)+ theme(plot.title = element_text(hjust = 0.5))
  
}
```


## Reading COMPUSTAT Data
Using haven library to read SAS dataset of COMPUSTAT
```{r}
data_path <- "D:\\Data\\funda.sas7bdat"
variables_path <- "D:\\Data\\required_variables.csv"
variables_to_take <- read.csv(variables_path,header=FALSE)
variables_list <- append(c('fyear', 'gvkey', 'tic','indfmt', 'conm' ,'scf', 'compst','sich','prcc_f','csho','re'),variables_to_take$V1) 
compustat_data <- haven::read_sas(data_path, col_select = variables_list)

compustat_data <- compustat_data %>% 
  filter(compst != "AB", !(sich %in% 4900:4999),!(sich %in% 6000:6999)) %>%   # financial firms, regulated utilities and firms in major M$As
  filter (scf != 4, scf != 5, scf != 6) %>%                                   # scf values filtered
  drop_na(scf, at) %>%
  filter(at != 0) %>%                                                         # filter to remove zero total assets
  select(-c(compst,sich)) 

```
## Calculating Fundamental Ratios And Saving Again
We add lags to the fundamental data as the data is relesead after a quarter of the actual realised results.
We avoid lookahead bias by doing so.
```{r}
compstat_data_to_save <- compustat_data %>%
  arrange(fyear) %>% group_by(cusip) %>%
  mutate(book_val = lag(at),
         investments = lag(ifelse(scf %in% c(1:3), capx+ivch+aqc+fuseo-sppe-siv, capx+ivch+aqc-sppe-siv-ivstch-ivaco)),
         net_cashflow = lag(fincf + ivncf + oancf),
         avg_at =  (at + ifelse(!is.na(lag(at)),lag(at),at))/2, 
         roa = lag(oiadp/avg_at)) %>%
  drop_na(investments,net_cashflow,revt,sale,dv,roa) %>%
  mutate(cashflows_trailing = rollapplyr(net_cashflow, 5, mean, na.rm = TRUE, fill = NA),
         revt_trailing = rollapplyr(lag(revt), 5, mean, na.rm = TRUE, fill = NA),
         sale_trailing = rollapplyr(lag(sale), 5, mean, na.rm = TRUE, fill = NA),
         div_trailing = rollapplyr(lag(dv), 5, mean, na.rm = TRUE, fill = NA),
         investment_trailing = rollapplyr(investments,5, mean, na.rm = TRUE, fill = NA),
         prof_trailing = rollapplyr(roa, 5, mean, na.rm = TRUE, fill = NA),
         asset_turnover = lag(sale/avg_at),
         altman = 1.2*(ifelse(at!=0,(act-lct)/at,NA))+1.4*(ifelse(at!=0,re/at,NA))+3.3*(ifelse(at!=0,oiadp/at,NA))+0.6*(ifelse(lt!=0,(prcc_f*csho)/lt,NA))+0.99*(ifelse(at!=0,sale/at,NA)),
        ohlson=-1.32-0.407*ifelse(at!=0,log(at),NA)+6.03*(ifelse(at!=0,lt/at,NA))-1.43*(ifelse(at!=0,(act-lct)/at,NA))+0.0757*(ifelse(act!=0,lct/act,NA))-2.37*(ifelse(at!=0,ni/at,NA))-1.83*(ifelse(lt!=0,(pi+dp)/lt,NA))-1.72*(ifelse(lt>at,1,0))+0.285*(ifelse((ni<0) && (ifelse(is.na(lag(ni)),ni,lag(ni)))<0,1,0))-0.521*ifelse(is.na(lag(ni)),0,((ni-lag(ni))/(abs(ni)+abs(lag(ni)))))) %>%
  select(c('fyear','cusip','mkvalt','conm','book_val', 'cashflows_trailing','revt_trailing','sale_trailing','div_trailing','investment_trailing','prof_trailing','asset_turnover',"net_cashflow", "revt", "sale", "at","altman","ohlson"))

```

## Reading Monthly CSRP Data
We read the CRSP monthly data and perform the neccessary mutations. WE lag the data by one month to avoid any lookahead bias.
```{r}
compstat_saved <- compstat_data_to_save %>%        ## We only use CUSIP that are present in Compustat
  mutate(cusip = str_sub(cusip,1,8)) %>%           ## Compustat ahs 9 digit cusip while CRSP has 8 digit cusip
  filter(fyear >= 1971)
    
monthly_data <- fread("D:\\Data\\msf_new2.csv") %>% 
  tibble() %>%
  filter (SHRCD %in% c(10,11), DATE > 19710000) %>%
  mutate(RET = as.numeric(RET)) %>%
  drop_na(RET) %>%
  mutate(DATE = as.Date(parse_date_time(DATE, orders = "Ymd")), DATE = floor_date(DATE, unit = "month"),
         PRC = ABS(PRC)) %>%
  inner_join(french_data) %>%
  mutate(excess_return = RET,
         mkt_excess_return = VWRETD,
         year = year(DATE))%>%
  arrange(DATE) %>%
  group_by(CUSIP) %>%
  mutate(excess_return = lag(excess_return),
         mkt_excess_return = lag(mkt_excess_return),
         ln_ret = lag(c(diff(log(PRC)),NA)))

yearly_returns <- monthly_data %>%
  ungroup() %>%
  group_by(CUSIP,year) %>%
  mutate(year = as.Date(paste(year, 1, 1, sep = "-"))) %>% 
  summarise(market_cum_return = prod(1+mkt_excess_return)-1,
            cum_excess_return = prod(1+excess_return)-1,
            cum_ln_ret = sum(ln_ret)) %>% ungroup()
```

## Fundamental Indexing
We calculate the rankings, cumulative returns for each rank pfolio, and plot in plotly as well as SHINY APP.
```{r}
rankandPlot <- function(compstat_saved, yearly_returns, variable){
  
  cum_returns <- getRankedStocks(compstat_saved, variable) %>%
                calcCumRets(yearly_returns,variable)

  cum_returns <- cum_returns %>% select(-c(Eq_cum_returns)) %>% pivot_wider(names_from = quintiles, values_from = Wtd_cum_return)
  
  plot_with_recession(cum_returns, paste(variable, " Based Portfolios"))
  data_plot(cum_returns, paste(variable, " Based Portfolios"))
  ## FOR SHINY APP UNCOMMENT THE BOTTOM PART
  
#   ui <- fluidPage(
#   selectInput("choice", "Choose", choices = names(cum_returns), selected = NULL),
#   plotlyOutput("graph")
#   )
# 
#   server <- function(input, output, session){
# 
#   output$graph <- renderPlotly({
#     plot_ly(cum_returns, x = ~year , y = ~get(input$choice), type = 'scatter', mode = 'markers')
#   })
# 
# }
}
rankandPlot_forcleandate <- function(compstat_saved, yearly_returns, variable) {
  
  cum_returns <- getRankedStocks_forcleandate(compstat_saved, variable) %>%
                calcCumRets(yearly_returns,variable) 

  cum_returns <- cum_returns %>% select(-c(Eq_cum_returns)) %>% pivot_wider(names_from = quintiles, values_from = Wtd_cum_return)
  
  ## SHINY APP IMPLEMENTATION
  ui <- fluidPage(
  selectInput("choice", "Choose", choices = names(cum_returns), selected = NULL),
  plotlyOutput("graph")
  )

  server <- function(input, output, session){

  output$graph <- renderPlotly({
    plot_ly(cum_returns, x = ~year , y = ~get(input$choice),  type = 'scatter', mode = 'markers')
  })
}

shinyApp(ui, server)

#data_plot(cum_returns, paste(variable, " Based Portfolios"))
}

rankandPlot(compstat_saved, yearly_returns, "book_val")
rankandPlot(compstat_saved %>% filter(cashflows_trailing != 0), yearly_returns, "cashflows_trailing")
rankandPlot(compstat_saved, yearly_returns, "revt_trailing")
rankandPlot(compstat_saved, yearly_returns, "sale_trailing")
rankandPlot(compstat_saved, yearly_returns, "div_trailing")
rankandPlot(compstat_saved, yearly_returns, "investment_trailing")
rankandPlot(compstat_saved, yearly_returns, "prof_trailing")
rankandPlot(compstat_saved, yearly_returns, "asset_turnover")
rankandPlot(compstat_saved, yearly_returns, "prof_trailing")
rankandPlot(compstat_saved, yearly_returns, "asset_turnover")
rankandPlot(compstat_saved, yearly_returns, "altman")
rankandPlot(compstat_saved, yearly_returns, "ohlson")
```

## Analysis of Portfolio Returns
This function returns the Annualized sharpe, std dev, skewness, kurtosis, information ratio's and so on, for each ranked protfolio.
We calculate this using the tidyquant library functions.
```{r}
calcStats <-function(compstat_saved, yearly_returns, variable){
  
    cum_returns <- getRankedStocks(compstat_saved, variable) %>%
      calcCumRets(yearly_returns,variable) %>%
      getReturns()%>%
      #select(-c(Eq_cum_returns)) %>% 
      pivot_wider(names_from = quintiles, values_from = Wtd_cum_return) 
    
    r1<- cum_returns%>% select(c("year","1")) %>% distinct() %>% drop_na() %>% mutate(ret = `1`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r1_<- cum_returns%>% select(c("year","1")) %>% distinct() %>% drop_na() %>% mutate(ret = `1`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r1__<- cum_returns%>% select(c("year","1","market_cum_return")) %>% filter(!is.na(`1`))%>% mutate(ret = `1`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)

    r1<- cbind(r1,r1_,r1__)
    
    r2<- cum_returns%>% select(c("year","2")) %>% distinct() %>% drop_na() %>% mutate(ret = `2`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r2_<- cum_returns%>% select(c("year","2")) %>% distinct() %>% drop_na() %>% mutate(ret = `2`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r2__<- cum_returns%>% select(c("year","2","market_cum_return")) %>% filter(!is.na(`2`))%>% mutate(ret = `2`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)
    r2<- cbind(r2,r2_,r2__)
    
    r3<- cum_returns%>% select(c("year","3")) %>% distinct() %>% drop_na() %>% mutate(ret = `3`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r3_<- cum_returns%>% select(c("year","3")) %>% distinct() %>% drop_na() %>% mutate(ret = `3`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r3__<- cum_returns%>% select(c("year","3","market_cum_return")) %>% filter(!is.na(`3`))%>% mutate(ret = `3`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)
    r3<- cbind(r3,r3_,r3__)
    
    r4<- cum_returns%>% select(c("year","4")) %>% distinct() %>% drop_na() %>% mutate(ret = `4`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r4_<- cum_returns%>% select(c("year","4")) %>% distinct() %>% drop_na() %>% mutate(ret = `4`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r4__<- cum_returns%>% select(c("year","4","market_cum_return")) %>% filter(!is.na(`4`))%>% mutate(ret = `4`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)
    r4<- cbind(r4,r4_,r4__)
    
    r5<- cum_returns%>% select(c("year","5")) %>% distinct() %>% drop_na() %>% mutate(ret = `5`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r5_<- cum_returns%>% select(c("year","5")) %>% distinct() %>% drop_na() %>% mutate(ret = `5`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r5__<- cum_returns%>% select(c("year","5","market_cum_return")) %>% filter(!is.na(`5`))%>% mutate(ret = `5`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)
    r5<- cbind(r5,r5_,r5__)
    
    r <- rbind(r1,r2,r3,r4,r5) 
    
    return(r)
}

x_bookval <-calcStats(compstat_saved, yearly_returns, "book_val")
x_cashflow <-calcStats(compstat_saved %>% filter(cashflows_trailing != 0), yearly_returns, "cashflows_trailing")
x_revenue <-calcStats(compstat_saved, yearly_returns, "revt_trailing")
x_sale <- calcStats(compstat_saved, yearly_returns, "sale_trailing")
#x_div <- calcStats(compstat_saved, yearly_returns, "div_trailing")
x_inv <- calcStats(compstat_saved, yearly_returns, "investment_trailing")
x_prof <- calcStats(compstat_saved, yearly_returns, "prof_trailing")
x_asset <- calcStats(compstat_saved, yearly_returns, "asset_turnover")

```

## Functions for rolling beta and annualized vols 
```{r}
#Compute beta by cov/var method
beta_compute <- function(x,y){
  cov(x,y)/var(y)
}

beta_daily_function = function(data,x,y, col_name) {
          
    data <-  data %>% group_by(CUSIP,BK_START) %>%
              summarise(Cor = cov(!!sym(x), !!sym(y))/var(!!sym(y)))
    names(data)[3] = col_name
    data
}

rolling_function = function(x,y,z,col_name){
  if(col_name == "roll_beta"){
      rolling <- rollify(function(x, y) {cov(x,y)/var(y)}, window = z)
      return(rolling(x,y))
  }
  else if(col_name == "annualised_vol"){rolling <- rollify(function(x) {sd(x)*sqrt(12)}, window = z)
  }
  else{
    rolling <- rollify(function(x) {sqrt(sum(x**2))},window = z)
  }
  return(rolling(x))
}

rolling_calculation <- function(data,window,col_name){
  
  stock_data_modified <- data%>% group_by(CUSIP)%>%
    filter(n() >= window)%>%
    arrange(DATE_START)%>%
    mutate(!!col_name := lag(rolling_function(RET,VWRETD,window,!!col_name)))%>%
    group_by(DATE_START)%>% 
    filter(month(DATE_START)==1)%>%
    drop_na(sym(col_name))
  return(stock_data_modified)
}

```

## Data for beta ranks
Re-reading monthly data in new envirnoment, and performing neccessary mutations.
```{r}
monthly_data <- fread("D:\\Data\\msf_new2.csv") %>% tibble() %>%
  filter(DATE>="19710000")

monthly_data_modified = monthly_data%>%
  arrange(CUSIP,DATE)%>%
  drop_na(PRC)%>%
  mutate(PRC = abs(PRC))%>%
  filter(SHRCD %in% c(10,11))%>%
  select(c(CUSIP,DATE,PRC,RET,VOL,SHROUT,VWRETD,SHRCD))%>%
  mutate(DATE = as.Date(parse_date_time(DATE, orders = "Ymd")),MKTCAP = abs(PRC*SHROUT),DATE_START = floor_date(DATE, unit = "month"))%>%
  mutate(across(c(RET),as.numeric))%>%
  group_by(CUSIP)%>%
  mutate(RET = PRC/lag(PRC)-1)%>%
  distinct(DATE,.keep_all = TRUE)%>%
  ungroup()

```

## Fama French Factors
We have already read the fama french factor data. We download the momentum csv and read those factor and merge it with french_dt.
```{r}
french_dt <-french_Data%>%
  mutate(DATE_START = as.Date(parse_date_time(DATE, orders = "Ym")))%>%
  drop_na(DATE_START)%>%
  mutate_if(is.character, as.numeric)

mom_data = read.csv("D:\\Data\\F-F_Momentum_Factor.csv",skip = 12)
names(mom_data)[1] = "DATE_START"
mom_data = mom_data%>%
  tibble()%>%
  mutate(DATE_START = as.Date(parse_date_time(DATE_START, orders = "Ym")))%>%
  drop_na(DATE_START)%>%
  mutate_if(is.character, as.numeric)

french_dt <- french_dt %>% merge(mom_data,by = "DATE_START")

french_dt[,2:ncol(french_dt)] = french_dt[,2:ncol(french_dt)]/100

monthly_data_modified_risk_free <- monthly_data_modified%>%
  tibble()%>%
  merge(french_dt,by = "DATE_START")%>%
  drop_na(RET)%>%
  arrange(CUSIP,DATE_START)

monthly_data_modified_risk_free = monthly_data_modified_risk_free%>%
  mutate(MKT = Mkt.RF+RF)%>%
  select(-c(Mkt.RF))

stock_data = monthly_data_modified_risk_free%>%
  select(DATE_START,CUSIP,RET,VWRETD)

beta_yearly = rolling_calculation(stock_data,12,"roll_beta")
vol_yearly = rolling_calculation(stock_data,12,"annualised_vol")
vol_yearly_squared = rolling_calculation(stock_data,12,"annualised_vol (Ri = 0)")
```

## Performing regression for each factor models

```{r}
calcRegression_for_4f<-function(data,frequency,col_name,target = c("VWRETD"),s = 3){
  regression_data_1 = data%>%
  mutate(value = floor_date(DATE_START, unit = frequency))%>%
  select(-c(DATE_START))%>%
  drop_na(RET)%>%
  pivot_wider(names_from = CUSIP, values_from = c(RET),values_fill = 0)%>%
  arrange(value)

  names(regression_data_1) = c(target,value,paste0("CUSIP_",colnames(regression_data_1[s:ncol(regression_data_1)])))
  depVars <- paste(c(colnames(regression_data_1[s:ncol(regression_data_1)])))
  models = regression_data_1 %>% group_by(value) %>%
    do(model = list(lm(formula(paste('cbind(',paste(depVars, collapse = ','),') ~ ',paste(target, collapse = '+'))),
                       na.action = na.exclude ,data = .)))

  mkt_beta = list(models$model[1][[1]][[1]]$coefficients[2,])

  smb_beta = list(models$model[1][[1]][[1]]$coefficients[3,])
  hml_beta = list(models$model[1][[1]][[1]]$coefficients[4,])

  mom_beta = list(models$model[1][[1]][[1]]$coefficients[4,])

  
  k = models$model[1][[1]][[1]]$residuals
  k1 = list(t(sqrt(colSums(k**2)*12/(12-length(target)-1))))
  for (i in 2:nrow(models)){

    mkt_beta = append(mkt_beta,list(models$model[i][[1]][[1]]$coefficients[2,]))
    smb_beta = append(smb_beta,list(models$model[i][[1]][[1]]$coefficients[3,]))
    hml_beta = append(hml_beta,list(models$model[i][[1]][[1]]$coefficients[4,]))

    mom_beta = append(mom_beta,list(models$model[i][[1]][[1]]$coefficients[5,]))

    k = models$model[i][[1]][[1]]$residuals
    k1 = append(k1,list(t(sqrt(colSums(k**2)/(12-length(target)-1)))))
  }
  a = list()

    mkt_beta  = as.tibble(do.call(rbind, mkt_beta))
    mkt_beta = cbind(models$value,mkt_beta)
    mkt_beta <- mkt_beta %>%
      tibble()%>%
      rename(value = "models$value")
    names(mkt_beta)[1] = col_name
    a = c(a,list(mkt_beta))
    smb_beta  = as.tibble(do.call(rbind, smb_beta))
    smb_beta = cbind(models$value,smb_beta)
    smb_beta <- smb_beta %>%
      tibble()%>%
      rename(value = "models$value")
    names(smb_beta)[1] = col_name
    hml_beta  = as.tibble(do.call(rbind, hml_beta))
    hml_beta = cbind(models$value,hml_beta) 
    hml_beta <- hml_beta %>%
      tibble()%>%
      rename(value = "models$value")
    names(hml_beta)[1] = col_name
    a = c(a,list(smb_beta),list(hml_beta))
    mom_beta  = as.tibble(do.call(rbind, mom_beta))
    mom_beta = cbind(models$value,mom_beta) 
    mom_beta <- mom_beta %>%
      tibble()%>%
      rename(value = "models$value")
    names(mom_beta)[1] = col_name
    a = c(a,list(mom_beta))

  root_sq_error = as.tibble(do.call(rbind, k1))
  root_sq_error = cbind(models$value,root_sq_error)

  root_sq_error <- root_sq_error %>% tibble()%>% rename(value = "models$value")
  names(root_sq_error)[1] = col_name
  return(list(a,root_sq_error))
}


calcRegression_for_CAPM<-function(data,frequency,col_name,target = c("VWRETD")){
  regression_data_1 = data%>%
  mutate(value = floor_date(DATE_START, unit = frequency))%>%
  select(-c(DATE_START))%>%
  drop_na(RET)%>%
  pivot_wider(names_from = CUSIP, values_from = c(RET),values_fill = 0)%>%
  arrange(value)

  names(regression_data_1) = c(target,value,paste0("CUSIP_",colnames(regression_data_1[s:ncol(regression_data_1)])))
  depVars <- paste(c(colnames(regression_data_1[s:ncol(regression_data_1)])))
  models = regression_data_1 %>% group_by(value) %>%
    do(model = list(lm(formula(paste('cbind(',paste(depVars, collapse = ','),') ~ ',paste(target, collapse = '+'))),
                       na.action = na.exclude ,data = .)))
  mkt_beta = list(models$model[1][[1]][[1]]$coefficients[2,])
  
  k = models$model[1][[1]][[1]]$residuals
  k1 = list(t(sqrt(colSums(k**2)*12/(12-length(target)-1))))
  for (i in 2:nrow(models)){
    mkt_beta = append(mkt_beta,list(models$model[i][[1]][[1]]$coefficients[2,]))

    k = models$model[i][[1]][[1]]$residuals
    k1 = append(k1,list(t(sqrt(colSums(k**2)/(12-length(target)-1)))))
  }
  a = list()
  mkt_beta  = as.tibble(do.call(rbind, mkt_beta))
  mkt_beta = cbind(models$value,mkt_beta)
  mkt_beta <- mkt_beta %>%
    tibble()%>%
    rename(value = "models$value")
  names(mkt_beta)[1] = col_name
  a = c(a,list(mkt_beta))
  
  root_sq_error = as.tibble(do.call(rbind, k1))
  root_sq_error = cbind(models$value,root_sq_error)

  root_sq_error <- root_sq_error %>% tibble()%>% rename(value = "models$value")
  names(root_sq_error)[1] = col_name
  return(list(a,root_sq_error))
}


calcRegression_for_3f<-function(data,frequency,col_name,target = c("VWRETD"),s = 3){
  regression_data_1 = data%>%
  mutate(value = floor_date(DATE_START, unit = frequency))%>%
  select(-c(DATE_START))%>%
  drop_na(RET)%>%
  pivot_wider(names_from = CUSIP, values_from = c(RET),values_fill = 0)%>%
  arrange(value)

  names(regression_data_1) = c(target,value,paste0("CUSIP_",colnames(regression_data_1[s:ncol(regression_data_1)])))
  depVars <- paste(c(colnames(regression_data_1[s:ncol(regression_data_1)])))
  models = regression_data_1 %>% group_by(value) %>%
    do(model = list(lm(formula(paste('cbind(',paste(depVars, collapse = ','),') ~ ',paste(target, collapse = '+'))),
                       na.action = na.exclude ,data = .)))

  mkt_beta = list(models$model[1][[1]][[1]]$coefficients[2,])
  smb_beta = list(models$model[1][[1]][[1]]$coefficients[3,])
  hml_beta = list(models$model[1][[1]][[1]]$coefficients[4,])

  
  k = models$model[1][[1]][[1]]$residuals
  k1 = list(t(sqrt(colSums(k**2)*12/(12-length(target)-1))))
  for (i in 2:nrow(models)){

    mkt_beta = append(mkt_beta,list(models$model[i][[1]][[1]]$coefficients[2,]))

    smb_beta = append(smb_beta,list(models$model[i][[1]][[1]]$coefficients[3,]))
    hml_beta = append(hml_beta,list(models$model[i][[1]][[1]]$coefficients[4,]))

    k = models$model[i][[1]][[1]]$residuals
    k1 = append(k1,list(t(sqrt(colSums(k**2)/(12-length(target)-1)))))
  }
  a = list()

  mkt_beta  = as.tibble(do.call(rbind, mkt_beta))
  mkt_beta = cbind(models$value,mkt_beta)
  mkt_beta <- mkt_beta %>%
    tibble()%>%
    rename(value = "models$value")
  names(mkt_beta)[1] = col_name
  a = c(a,list(mkt_beta))
  smb_beta  = as.tibble(do.call(rbind, smb_beta))
  smb_beta = cbind(models$value,smb_beta)
  smb_beta <- smb_beta %>%
    tibble()%>%
    rename(value = "models$value")
  names(smb_beta)[1] = col_name
  hml_beta  = as.tibble(do.call(rbind, hml_beta))
  hml_beta = cbind(models$value,hml_beta) 
  hml_beta <- hml_beta %>%
    tibble()%>%
    rename(value = "models$value")
  names(hml_beta)[1] = col_name
  a = c(a,list(smb_beta),list(hml_beta))


  root_sq_error = as.tibble(do.call(rbind, k1))
  root_sq_error = cbind(models$value,root_sq_error)

  root_sq_error <- root_sq_error %>% tibble()%>% rename(value = "models$value")
  names(root_sq_error)[1] = col_name
  return(list(a,root_sq_error))
}
```

## Calling Regression function and storing CAPM Beta and RSE errors.
```{r}
c(capm_Beta,capm_RSE) %<-% 
  calcRegression_for_CAPM((monthly_data_modified_risk_free%>%
  select(DATE_START,CUSIP,RET,VWRETD)),"12month","YEAR_START")

c(betas_ff3,rse_market_ff3) %<-% 
  calcRegression_for_3f((monthly_data_modified_risk_free%>%
  select(DATE_START,CUSIP,RET,SMB,HML,VWRETD)),"12month","YEAR_START",c("VWRETD","SMB","HML"))

c(betas_ff4,rse_market_ff4) %<-% 
  calcRegression_for_4f((monthly_data_modified_risk_free%>%
  select(DATE_START,CUSIP,RET,SMB,HML,VWRETD,Mom)),"12month","YEAR_START",c("VWRETD","SMB","HML","Mom"))

c(beta_market_ff4,beta_smb_ff4,beta_hml_ff4,beta_mom_ff4) %<-% betas_ff4
c(beta_market_ff3,beta_smb_ff3,beta_hml_ff3) %<-% betas_ff3
beta_market_capm = capm_Beta[[1]]

beta_market_capm_1 <- beta_market_capm %>% 
  pivot_longer(!YEAR_START,names_to = "CUSIP",values_to = "beta_regression") %>% 
  rename(DATE_START = YEAR_START) %>%
  mutate(CUSIP = str_remove(CUSIP,"CUSIP_"))

capm_RSE_1 <- capm_RSE %>% 
  pivot_longer(!YEAR_START,names_to = "CUSIP",values_to = "IdioSyncratic Volatility for CAPM") %>% 
  rename(DATE_START = YEAR_START) %>%
  mutate(CUSIP = str_remove(CUSIP,"CUSIP_"))

rse_ff3_1 <- rse_market_ff3 %>% 
  pivot_longer(!YEAR_START,names_to = "CUSIP",values_to = "IdioSyncratic Volatility for 3 Factor Model") %>% 
  rename(DATE_START = YEAR_START) %>%
  mutate(CUSIP = str_remove(CUSIP,"CUSIP_"))

rse_ff4_1 <- rse_market_ff4 %>% 
  pivot_longer(!YEAR_START,names_to = "CUSIP",values_to = "IdioSyncratic Volatility for 4 Factor Model") %>% 
  rename(DATE_START = YEAR_START) %>%
  mutate(CUSIP = str_remove(CUSIP,"CUSIP_"))

beta_joined_data <- beta_market_capm_1%>% merge(beta_yearly,by = c("DATE_START","CUSIP"))
beta_joined_data <- capm_RSE_1%>% merge(beta_joined_data,by = c("DATE_START","CUSIP"))
beta_joined_data <- rse_ff3_1%>% merge(beta_joined_data,by = c("DATE_START","CUSIP"))
beta_joined_data <- rse_ff4_1%>% merge(beta_joined_data,by = c("DATE_START","CUSIP"))

rankandPlot_forcleandate(beta_yearly %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "roll_beta")
rankandPlot_forcleandate(vol_yearly %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "annualised_vol")
rankandPlot_forcleandate(vol_yearly_squared %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "annualised_vol (Ri = 0)")
rankandPlot_forcleandate(beta_joined_data %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "beta_regression")
rankandPlot_forcleandate(beta_joined_data %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "IdioSyncratic Volatility for CAPM")
rankandPlot_forcleandate(beta_joined_data %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "IdioSyncratic Volatility for 3 Factor Model")
rankandPlot_forcleandate(beta_joined_data %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "IdioSyncratic Volatility for 4 Factor Model")
```

## Analysis for beta based pfolios
```{r}
calcStats_forcleandate <-function(compstat_saved, yearly_returns, variable){
  
    cum_returns <- getRankedStocks_forcleandate(compstat_saved, variable) %>%
      calcCumRets(yearly_returns,variable) %>%
      getReturns()%>%
      select(-c(Eq_cum_returns)) %>% 
      pivot_wider(names_from = quintiles, values_from = Wtd_cum_return) 
    
    r1<- cum_returns%>% select(c("year","1")) %>% distinct() %>% drop_na() %>% mutate(ret = `1`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r1_<- cum_returns%>% select(c("year","1")) %>% distinct() %>% drop_na() %>% mutate(ret = `1`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r1__<- cum_returns%>% select(c("year","1","market_cum_return")) %>% filter(!is.na(`1`))%>% mutate(ret = `1`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)

    r1<- cbind(r1,r1_,r1__)
    
    
    r2<- cum_returns%>% select(c("year","2")) %>% distinct() %>% drop_na() %>% mutate(ret = `2`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r2_<- cum_returns%>% select(c("year","2")) %>% distinct() %>% drop_na() %>% mutate(ret = `2`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r2__<- cum_returns%>% select(c("year","2","market_cum_return")) %>% filter(!is.na(`2`))%>% mutate(ret = `2`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)
    r2<- cbind(r2,r2_,r2__)
    
    r3<- cum_returns%>% select(c("year","3")) %>% distinct() %>% drop_na() %>% mutate(ret = `3`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r3_<- cum_returns%>% select(c("year","3")) %>% distinct() %>% drop_na() %>% mutate(ret = `3`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r3__<- cum_returns%>% select(c("year","3","market_cum_return")) %>% filter(!is.na(`3`))%>% mutate(ret = `3`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)
    r3<- cbind(r3,r3_,r3__)
    
    r4<- cum_returns%>% select(c("year","4")) %>% distinct() %>% drop_na() %>% mutate(ret = `4`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r4_<- cum_returns%>% select(c("year","4")) %>% distinct() %>% drop_na() %>% mutate(ret = `4`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r4__<- cum_returns%>% select(c("year","4","market_cum_return")) %>% filter(!is.na(`4`))%>% mutate(ret = `4`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)
    r4<- cbind(r4,r4_,r4__)
    
    r5<- cum_returns%>% select(c("year","5")) %>% distinct() %>% drop_na() %>% mutate(ret = `5`)%>%
      tq_performance(Ra = ret, Rb = NULL, performance_fun = table.AnnualizedReturns)
    r5_<- cum_returns%>% select(c("year","5")) %>% distinct() %>% drop_na() %>% mutate(ret = `5`)%>%
    tq_performance(Ra = ret, Rb = NULL, performance_fun = table.Stats) %>% select(c(Skewness,Kurtosis))
    r5__<- cum_returns%>% select(c("year","5","market_cum_return")) %>% filter(!is.na(`5`))%>% mutate(ret = `5`)%>%
    tq_performance(Ra = ret, Rb = market_cum_return, performance_fun = table.InformationRatio)
    r5<- cbind(r5,r5_,r5__)
    
    r <- rbind(r1,r2,r3,r4,r5) 
    
    return(r)
}

x_beta <-calcStats_forcleandate(beta_yearly %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "roll_beta")
x_vol <-calcStats_forcleandate(vol_yearly %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "annualised_vol")
x_vol_0 <-calcStats_forcleandate(vol_yearly_squared %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "annualised_vol (Ri = 0)")
x_idio_capm <- calcStats_forcleandate(beta_joined_data %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "IdioSyncratic Volatility for CAPM")
x_idio_3f <- calcStats_forcleandate(beta_joined_data %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "IdioSyncratic Volatility for 3 Factor Model")
x_idio_4f <- calcStats_forcleandate(beta_joined_data %>% rename(fyear = DATE_START, cusip = CUSIP), yearly_returns, "IdioSyncratic Volatility for 3 Factor Model")

```

## SHINY APP TEMPLATE
ui has prompts like choice which wait for user input.
user input goes to the server and render plot according to the input variable.

```{r}
library(shiny)
library(plotly)

ui <- fluidPage(
  selectInput("choice", "Choose", choices = names(beta_joined_data), selected = NULL),
  plotlyOutput("graph")
  )

server <- function(input, output, session){

  output$graph <- renderPlotly({
    plot_ly(beta_joined_data, x = ~get(input$choice), y = ~RET, type = 'scatter', mode = 'markers')
  })
}

shinyApp(ui, server)
```


